---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nagerdate

<!-- badges: start -->
<!-- badges: end -->

The goal of nagerdate is to create a convenient API wrapper to the [Nager.Date](https://github.com/nager/Nager.Date) API. 

The Nager.Date API has an interface for getting holidays for a long list of countries for these holiday variants below:

- Public holidays
- Bank holidays
- School holidays
- Authority holidays
- Optional holidays where most people take a day off
- Observance holidays for optional festivities.


## Installation

You can install the development version of nagerdate like so:

``` r
remotes::install_github("krose/nagerdate")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(nagerdate)

# Get the suported countries
head(nd_available_countries())

# Get the country info for Germany
head(nd_country_info(country_code = "DE"))

# Get the holidays for Germany in 2023
head(nd_holidays(country_code = "DE", year = 2023))

```

